Title

### 2014-07-18 paper.tex
add results

\subsection{Data Preprocessing}

The commit messages and all comment texts are converted into vectors as part of the preprocessing step.
We wrote scripts in Ruby language to perform these tasks.

@@

\subsubsection{Stop word removal and stemming}

After the automatically generated messages are removed, we extracted the words by searching for alphanumeric characters and apostrophe, removed the stop words by using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}, and put the remaining words through Porter stemming algorithm.
The remaining words are then combined to form a corpus of all used words.

@@

% validation
To validate our model, 10-fold cross validation is used.
The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged.

@@

\subsection{Common Patterns}

The common patterns are found such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.

>>>>

\subsection{Data Preparation}

The commit messages and all comment texts are converted into vectors as part of the preparation step.
We wrote scripts in Ruby language to perform these tasks.

@@

\subsubsection{Tokenizing, stop word removal and stemming}

After the automatically generated messages are removed, we extracted the words in each document into a list of tokens by searching for alphanumeric characters including apostrophes.
Stop words from the Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}} are then removed.
The stemming is performed on remaining tokens using Porter stemming algorithm.
The remaining words are then combined to form a corpus of all used words.

@@

% validation
To validate our model, 10-fold cross validation is performed.
The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
to give the overall performance of our model.

@@

\subsection{Data Preparation}

In total, there are 6,605 changes and 72,484 comments. 25,076 comments are by the system or one of the bots.

\subsubsection{Common pattern removal}

Many common patterns are found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
The occurrences of these patterns are removed from our data set.
This leaves 36,738 comments empty, which probably means that the whole comment is automatically generated.
Only 17,275 comments and commit messages are left.

\subsubsection{Tokenizing}

After preprocessing, 393,238 tokens are generated in total. They are composed of 20,025 different words.
This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.
